---
title: "Part I Explorer"
output: html_notebook
---
# Chapter 3 : Introduction

install.packages("tidyverse")

library(tidyverse)

Data-Frame > mpg

```{r}
mpg

```

```{r}
?mpg

```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 0.5) + geom_smooth()


```

3.2.4 Exercises
Run ggplot(data = mpg). What do you see? BLANK

How many rows are in mpg? How many columns? 234, 11

What does the drv variable describe? Read the help for ?mpg to find out. f = front-wheel drive, r = rear wheel drive, 4 = 4wd

Make a scatterplot of hwy vs cyl.

What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

```{r}
ggplot(data = mpg)
```

structure of data mpg
```{r}
str(mpg)
```


Make a scatterplot of hwy vs cyl
```{r}
ggplot(data = mpg, aes(x = hwy, y = cyl)) +
  geom_point(size = 0.5) 
```

What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

two variable are factor variable

```{r}
ggplot(data = mpg, aes(x = class, y = drv)) +
  geom_point() 
```
while defining color it should be in aes(color = class).... 
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 1, aes(color = class))
```


```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = class)
```















