---
title: "Part I Explorer"
output:
  html_document:
    df_print: paged
---
# Chapter 3 : Introduction

install.packages("tidyverse")

library(tidyverse)

Data-Frame > mpg

```{r}
library(tidyverse)

```

```{r}
?mpg

```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 0.5) + geom_smooth()


```

3.2.4 Exercises
Run ggplot(data = mpg). What do you see? BLANK

How many rows are in mpg? How many columns? 234, 11

What does the drv variable describe? Read the help for ?mpg to find out. f = front-wheel drive, r = rear wheel drive, 4 = 4wd

Make a scatterplot of hwy vs cyl.

What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

```{r}
ggplot(data = mpg)
```

structure of data mpg
```{r}
str(mpg)
```


Make a scatterplot of hwy vs cyl
```{r}
ggplot(data = mpg, aes(x = hwy, y = cyl)) +
  geom_point(size = 0.5) 
```

What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

two variable are factor variable

```{r}
ggplot(data = mpg, aes(x = class, y = drv)) +
  geom_point() 
```
while defining color it should be in aes(color = class).... 
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 1, aes(color = class))
```


```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(size = class))
```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(color = "green")
```


```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(shape = class))
```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy, alpha = class)) +
  geom_point()
```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(shape = 22)
```


What’s gone wrong with this code? Why are the points not blue?

blue  should not be within aes as it is not defining a particular variable 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?


manufacturer
model----- catergorical
model name  ---- categorical

displ
engine displacement, in litres----continuous

year
year of manufacture---- categorical

cyl
number of cylinders----- continuous

trans
type of transmission----- categorical

drv
f = front-wheel drive, r = rear wheel drive, 4 = 4wd----categorical

cty
city miles per gallon---- continuous

hwy
highway miles per gallon ---- continuous

fl
fuel type---- categorical

class
"type" of car----- categorical
```{r}
str(mpg)
```


-------------------------------------------------------------------------
Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

```{r}
ggplot(data = mpg) + geom_point(aes(x = displ, y = hwy, color = class, size = class, shape = class))
```






What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg, aes(x = cty, y = cty)) +
  geom_point()
```

What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

-- stroke asthetic is used to modify the width of the border.
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 5, shape = 6, stroke = 3)
```


6. 
What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.

ans:
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 1, aes(color = displ < 5 ))
```

































