---
title: "Part I Explorer"
output:
  html_document:
    df_print: paged
---
# Chapter 3 : Introduction

install.packages("tidyverse")

library(tidyverse)

Data-Frame > mpg

```{r}
library(tidyverse)

```

```{r}
?mpg

```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 0.5) + geom_smooth()


```

3.2.4 Exercises
Run ggplot(data = mpg). What do you see? BLANK

How many rows are in mpg? How many columns? 234, 11

What does the drv variable describe? Read the help for ?mpg to find out. f = front-wheel drive, r = rear wheel drive, 4 = 4wd

Make a scatterplot of hwy vs cyl.

What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

```{r}
ggplot(data = mpg)
```

structure of data mpg
```{r}
str(mpg)
```


Make a scatterplot of hwy vs cyl
```{r}
ggplot(data = mpg, aes(x = hwy, y = cyl)) +
  geom_point(size = 0.5) 
```

What happens if you make a scatterplot of class vs drv? Why is the plot not useful?

two variable are factor variable

```{r}
ggplot(data = mpg, aes(x = class, y = drv)) +
  geom_point() 
```
while defining color it should be in aes(color = class).... 
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 1, aes(color = class))
```


```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(size = class))
```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(color = "green")
```


```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(shape = class))
```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy, alpha = class)) +
  geom_point()
```

```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(shape = 22)
```


What’s gone wrong with this code? Why are the points not blue?

blue  should not be within aes as it is not defining a particular variable 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?


manufacturer
model----- catergorical
model name  ---- categorical

displ
engine displacement, in litres----continuous

year
year of manufacture---- continuous

cyl
number of cylinders----- continuous

trans
type of transmission----- categorical

drv
f = front-wheel drive, r = rear wheel drive, 4 = 4wd----categorical

cty
city miles per gallon---- continuous

hwy
highway miles per gallon ---- continuous

fl
fuel type---- categorical

class
"type" of car----- categorical
```{r}
str(mpg)
```


-------------------------------------------------------------------------
Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

```{r}
ggplot(data = mpg) + geom_point(aes(x = displ, y = hwy, color = class, size = class, shape = class))
```






What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = cyl, size = hwy, shape = drv))
```

What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

-- stroke asthetic is used to modify the width of the border.
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 5, shape = 6, stroke = 3)
```


6. 
What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.

ans:
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(size = 1, aes(color = displ < 5 ))
```


```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap( ~ class, ncol = 4)
```



```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(. ~ cty)
```


Exercise

What happens if you facet on a continuous variable?

Ans:
There is one facet for each value e.g. a facet on displ.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy)) +
  facet_wrap(~ displ)
```

2. What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
The facets are empty when there is no data for the according combination e.g. rear wheel drive (r) with 4 or 5 cylinder is not listed. The 7 cylinder factes are missed entirely.

Ans:

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ cyl)
```

3. What plots does the following code make? What does . do?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid( ~ drv)
```

4. Take the first faceted plot in this section. What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))

```



```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```


5. Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?

```{r}
?facet_wrap
```



6. When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?


```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(class ~ drv)
```

```{r}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv))
```



```{r}
ggplot(data = mpg) + geom_point(aes(x = displ, y = hwy, color = drv)) +
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv))


```


```{r}
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
              
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv))
    
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, color = drv),show.legend = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(aes(color = class),show.legend = FALSE) + 
  geom_smooth()
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth(data = filter(mpg, class == "suv"), se = FALSE)
```

```{r}
?geom_smooth
```
EXCERCISE
 
1. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart? 
 
 

 
 2. Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```
 Didn’t expected that there would be multiple lines. Maybe because grouped by “color = drv”.
 
 
 3. What does show.legend = FALSE do? What happens if you remove it? Why do you think I used it earlier in the chapter?
Actually, never used before, but in 3.9 coordinate systems.

4. What does the se argument to geom_smooth() do?
Shows the confidence interval around the line. (the grey area)

5. Will these two graphs look different? Why/why not?
No, because the layers inherit the configuration from ggplot.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()
```

 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 